### 2013-07-10 inst/doc/reml.Rmd
writing outline

The Ecological Metadata Language

@@

[Jones 2006]: http://dx.doi.org/10.1146/annurev.ecolsys.37.091305.110031
[KNB]: http://knb.ecoinformatics.org
[Berkley 2001]: http://dx.doi.org/10.1109/4236.957896
[Michener 1997]: http://dx.doi.org/10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2
[Morell 1996]: http://dx.doi.org/10.1126/science.273.5275.569
[Canhos 2004]: https://journals.ku.edu/index.php/jbi/article/viewArticle/3

>>>>

Unfortunately, adoption of these metadata standards for annotating research
data has been limited, owing to both technological and social challenges 
involved [Reichman 2011].

Things to discuss:

*  It's not just a problem of sharing culture 
* Sharing is not effective: close competitors can scoop you, but broader reach can't be realized without good metadata 
* [Strasser survey showing lagging data management practices]
* [Stodden survey showing effort in curating data is a barrier]

@@

[Reichman 2011]: http://dx.doi.org/10.1126/science.1197962
[Jones 2006]: http://dx.doi.org/10.1146/annurev.ecolsys.37.091305.110031
[KNB]: http://knb.ecoinformatics.org
[Berkley 2001]: http://dx.doi.org/10.1109/4236.957896
[Michener 1997]: http://dx.doi.org/10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2
[Morell 1996]: http://dx.doi.org/10.1126/science.273.5275.569
[Canhos 2004]: https://journals.ku.edu/index.php/jbi/article/viewArticle/3

[Michener 2006]: http://dx.doi.org/10.1016/j.ecoinf.2005.08.004
[Michener 2012]: http://dx.doi.org/10.1016/j.tree.2011.11.016
